---
title: "Atividades"
output_dir: "docs"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```

## Relembrando a estatística geral

## Delineamento inteiramente casualizado

### Croqui 

Escreva o código para gerar um croqui de 7 tratamentos e 5 repetições em dic. 

```{r A1, exercise=TRUE}

```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Comparação de médias

## Pressuposições da ANOVA

## Regressão polinomial

## Delineamento em blocos casualizados 

### Croqui 

Escreva o código para gerar um croqui de 5 tratamentos e 5 repetições em dbc. 

```{r A2, exercise=TRUE}

```


## Delineamento quadrado latino 

### Croqui 

Escreva o código para gerar um croqui de 6 tratamentos em dql. 

```{r A3, exercise=TRUE}

```



## Esquema fatorial

### Croqui 

Um experimento será realizado em casa de vegetação visando estabelecer a relação entre genótipos de batatas e diferentes doses de Uréia a ser aplicada. Para isso o pesquisador pede que você desenhe um possível croqui para esse experimento. Serão utilizados 4 genótipos e 4 doses de uréia. Escreva o código para gerar um croqui. 


```{r A4, exercise=TRUE}

```


## Esquema parcelas subdivididas

### Croqui 

Um experimento será realizado em campo visando estabelecer a relação entre diferentes cortes de cana (cana planta e cana soca) e diferentes métodos de sulcos (simples e duplo). Para isso o pesquisador pede que você desenhe um possível croqui para esse experimento. Serão utilizados 10 repetições. Escreva o código para gerar um possível croqui. 


```{r A5, exercise=TRUE}

```



### Exercise with Hint

*Here's an exercise where the chunk is pre-evaluated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

